An Incomplete Overview of some Applications of Game Theory to Patient Flow

### 2014-05-12 paper.tex
structure with stuff

In \cite{} various theoretical results are proven.

@@

\begin{itemize}
    \item IK Paper
\end{itemize}

@@

\begin{itemize}
    \item Describe model;
    \item Show some results.
\end{itemize}

>>>>

In \cite{} various theoretical results are proven. With regards to the effect of worth of service on the PoA but also with regards to demand. The profile of Figure \ref{fig:poaprofile} is shown to hold in general.

\begin{figure}[!hbtp]
Pic
\end{figure}

To consider systems where individuals are able to observe the system there are two approaches: the first is to use a simulation based approach that allows individuals to choose their most desirable queue.
One such approach that was considered specifically in the context of healthcare was considered in \cite{}.

Given that individuals will consider a simple selfish decision rule this approach is relatively straightforward and can also be considered using straightforward analytical Markov models.
The difficulty with this approach is appears when attempting to obtain the PoA.
To carry this out an optimal policy must be obtained.

In \cite{} various dynamic programming and approximate dynamic programming techniques are proposed that are able to not only give an optimal policy but also prove the following observation:

\begin{center}
\textit{Selfish users make busier systems.}
\end{center}

In the next section selfish congestion related decisions by managers will be considered.

@@

Talk about idea.
Talk about Markov model.
Talk about proof that pure strategy NE exists.
Show how can be used to influence t.

@@

Describe simple Markov model for hospital.
Describe routing game model for thing.
